\documentclass[11pt]{article}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{graphicx,DCCN2019_en}

\pagestyle{fancy}
\fancyhead{} 
\fancyfoot{}

\usepackage[utf8]{inputenc}
\linespread{1.0}

\usepackage{amsmath}

\makeatletter
\fancyhead[RO]{\small DCCN 2019 \\ {23-27 September 2019}}
\fancyhead[LO]{\small Ketipov, Kostadinov, Petrov, Zankinski, Balabanov \\ Human-Computer MDC for TS Forecasting}
% Rumen Ketipov
% Georgi Kostadinov
% Plamen Petrov
% Iliyan Zankinski
% Todor Balabanov

\c@page=1 
       
\makeatother

\title{Human-Computer Mobile Distributed Computing for Time Series Forecasting}

\author[1]{\small R.R. Ktipov}
\author[1]{\small G.B. Kostadinov}
\author[1]{\small P.D. Petrov}
\author[1]{\small \\I.A. Zankinski}
\author[0000-0003-3139-069X]{\small T.D. Balabanov}

\affil[1]{\footnotesize Institute of Information and Communication Technologies \break Bulgarian Academy of Sciences \break acad. Georgi Bonchev Str., block 2, office 514, 1113 Sofia, Bulgaria}

\email{rketipov@iit.bas.bg, g.kostadinov@iit.bas.bg, p.petrov@iit.bas.bg, iliyan@hsi.iccs.bas.bg, todorb@iinf.bas.bg}

\begin{document}

\udc{004.93}

{\let\newpage\relax\maketitle}

\vskip -1.5em

\footnotetext{This work was supported with private funding by Velbazhd Software LLC.}

\begin{abstract}
Distributed computing became very popular in the last two decades. In many cases distributed computing projects are based on a donated calculation power. The most famous donated distributed computing project is SETI@home, which is related to deep space signals processing in attempt to find an alien life. The usage of donated distributed computing had its influence in the time series forecasting in the face of MoneyBee\cite{bohn01} project. MoneyBee project was a desktop screensaver application, which was calculating financial time series forecasting by training of artificial neural networks with evolutionary algorithms. With the expansion of the mobile devices in last decade it become relevant some donated distributed computing solutions to be developed as mobile applications. Such solution was developed at IICT-BAS\cite{tomov01}, which is based on Android Live Wallpaper technology. This research proposes an extension of the work done at IICT-BAS in the direction of human-computer based distributed computing by providing software capabilities of the users to vote for future financial changes. 

\keywords{distributed computing, time series forecasting, artificial neural networks, evolutionary algorithms}
\end{abstract}

\section{Introduction} \label{Introduction}

Financial time series forecasting is an attractive and intensively researched area. One of the most interesting research directions in this field is related to the usage of artificial neural networks combined with evolutionary algorithms. In some studies evolutionary algorithms are used for artificial neural network topology optimization, but in other studies evolutionary algorithms are used for artificial neural network weights optimization. When evolutionary algorithms are used for weights optimization it is very common the training to be combined with back-propagation algorithm. Even when such hybrid training algorithm is used it is in the class of supervised training. Training examples are fed to the artificial neural network and its weights are modified according the selected training algorithm. Evolutionary algorithms have a common advantage compared to the exact numerical methods and it is the possibility for parallel calculations. When the parallel calculations are done on separate mobile devices it is the case of mobile distributed computing. It is very common the financial forecasting to be done by the usage of the past values in the time series, but it can be combined with human evaluation of the future values. In this research human-computer based mobile distributed computing solution is proposed. The users are using Android application, which trains artificial neural network with evolutionary algorithms and back-propagation, but users are capable to vote for increase or decrease of the future values. The most successful forecast votes of the users are used in artificial neural network training process.

\section{Model Proposition} \label{Model Proposition}

\section{Experiments and Results} \label{Experiments and Results}

\section{Conclusion} \label{Conclusion}

\vskip 1.5em

\begin{thebibliography}{99}

\bibitem{bohn01} Bohn, A., Guting, T., Mansmann, T., \textbf{\textit{MoneyBee: A new product to predict stock market developments using artificial intelligence and increased calculation capacitiy}} (in German), et al. Wirtschaftsinf, vol. 45, no. 3, p. 325--333, 2003.

\bibitem{tomov01} Tomov, P., Zankinski, I., Barova, M., \textbf{\textit{Mobile Alternative of the MoneyBee Project for Financial Forecasting}}, Proceedings of the Annual University Scientific Conference of the National Military University Vasil Levski, Veliko Tarnovo, p. 1085--1089, 2018.

\end{thebibliography}

\end{document}
